\documentclass{beamer}

\usetheme{Madrid}
\usecolortheme{beaver}

\title{MetaTrace: Web-Based Metadata Forensics Tool}
\subtitle{Progress Presentation}
\author{WE Group 12}
\date{\today}

\begin{document}

% Title Slide
\begin{frame}
    \titlepage
\end{frame}

% Slide 2: Problem Statement
\begin{frame}{Problem Statement}
    \begin{itemize}
        \item \textbf{Importance of Metadata:}
        \begin{itemize}
            \item Critical for verifying file authenticity, ensuring data integrity, and supporting investigations.
            \item Offers insights into file origins, modifications, and hidden data.
        \end{itemize}
        \item \textbf{Challenges with Existing Tools:}
        \begin{itemize}
            \item Advanced tools like ExifTool require deep technical expertise.
            \item Lack integrated visualization and intuitive, predictive analytics.
            \item Limited accessibility for non-technical users, hindering broader adoption.
        \end{itemize}
    \end{itemize}
\end{frame}

% Slide 3: Proposed Solution
\begin{frame}{Proposed Solution}
    \textbf{MetaTrace: A Comprehensive Metadata Analysis Platform}
    \begin{itemize}
        \item \textbf{User-Friendly Interface:} A web-based tool that simplifies metadata extraction, visualization, and analysis.
        \item \textbf{Broad File Format Support:} Extracts metadata from images, documents, multimedia files, and more.
        \item \textbf{Advanced Analytics:}Predictive insights and anomaly detection.
        \item \textbf{Empowering Users:} Makes metadata accessible for both technical experts and non-technical users to verify authenticity, trace leaks, and investigate cybercrimes.
    \end{itemize}
\end{frame}


% Slide 4: Key Features
\begin{frame}{Key Features}
    \begin{enumerate}
        \item \textbf{File Upload:} Supports images, PDFs, and documents.
        \item \textbf{Metadata Extraction:} Uses ExifTool for detailed metadata analysis.
        
        \item \textbf{Predictive Insights:} Detect anomalies in metadata.
        \item \textbf{Searchable Storage:} Fast and scalable metadata search.
    \end{enumerate}
\end{frame}



% Slide 6: Feasibility & Technology
\begin{frame}{Tech Stack}
    \textbf{Technology Stack:}
    \begin{itemize}
        \item \textbf{Frontend:} Next.js, Tailwind CSS
        \item \textbf{Backend:} Python with FastAPI and ExifTool integration.
        \item \textbf{Database:} MongoDB
    \end{itemize}
\end{frame}

% Slide 7: Potential Impact
\begin{frame}{Current Progress}
    \begin{itemize}
       \item \textbf{Completed:}
        \begin{itemize}
            
            \item File validations
            \item Frontend using Nextjs and Tailwind CSS
            \item Backend using FastAPI
            \item Metadata extraction functionality
            \item Database setup using MongoDB
        \end{itemize}
         \item \textbf{Ongoing:}
        \begin{itemize}
            \item Exploring deeper metadata extraction
            \item JWT authentication for login
            \item Investigating anomaly detection possibilities     
        \end{itemize}
        \item \textbf{Next Steps:}
        Integration and optimization        
           
        
    \end{itemize}
\end{frame}

\begin{frame}{Timeline}
    \begin{itemize}    
           \item \textbf{Completed:}
        \begin{itemize}
            \item Week 1, Dec 2024 – Research \& approval 
            \item Week 2, Dec 2024 – Project planning \& task allocation
            \item Week 3, Dec 2024 – Secondary approval 
            \item Week 4, Dec 2024 – UX design \& ExifTool documentation
            \item Weeks 1–3, Jan 2025 – Frontend \& backend development 
            \item Week 4, Jan 2025 – Metadata extraction; integration failed
            
        \end{itemize}
        \item \textbf{Upcoming:}
        \begin{itemize}
            \item Week 5, 2nd week of Feb, 2025: JWT Authentication for login
            \item Week 6, 3rd week of Feb, 2025: Integration \& Testing
            \item Week 7, 4th week of Feb, 2025: Optimization
        \end{itemize}
    \end{itemize}
\end{frame}

\begin{frame}{DEMO}
\begin{center}
        \textbf{Demo!}\\        
    \end{center}
    \vspace{1cm}
    
\end{frame}

\begin{frame}{Challenges and Learnings}
    \begin{itemize}
        \item \textbf{Challenges:}
        \begin{itemize}
            \item Metadata variations across file formats
            \item Ensuring accurate extraction
            \item Balancing speed and performance
        \end{itemize}
        \item \textbf{Learnings:}
        \begin{itemize}
            \item FastAPI is efficient for handling metadata extraction
            \item Tailwind CSS simplifies frontend development
            \item Need for thorough testing before integration
        \end{itemize}
    \end{itemize}
\end{frame}

\begin{frame}{Thank you}
\begin{center}
        \textbf{Thank you for your time and consideration!}\\        
    \end{center}
    \vspace{1cm}
    \begin{flushright}
        \textit{WE Group 12}
    \end{flushright}
\end{frame}


\end{document}
